Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-02-08 paper-ieee-trans.tex
online references aligned

\bibitem{cordis:datagrid}
\emph{DataGrid project}, European Community Research and Development
Information Service (CORDIS),
http://cordis.europa.eu/project/rcn/53665\_en.html

@@

\bibitem{agile-manifesto}
\emph{Manifesto for Agile Software Development}, http://agilemanifesto.org

@@

\bibitem{cordis:egee}
\emph{Enabling Grids for E-sciencE (EGEE)} project, European Community
Research and Development Information Service (CORDIS),
http://cordis.europa.eu/project/rcn/80149\_en.html

\bibitem{cordis:egee2}
\emph{Enabling Grids for E-sciencE-II (EGEE-II)} project, European Community
Research and Development Information Service (CORDIS),
http://cordis.europa.eu/project/rcn/99189\_en.html

\bibitem{cordis:egee3}
\emph{Enabling Grids for E-sciencE-III (EGEE-III)} project, European Community
Research and Development Information Service (CORDIS),
http://cordis.europa.eu/project/rcn/87264\_en.html

\bibitem{egee:acceptance-criteria}
\emph{Definition and Documentation of the Revised Software Life-Cycle Process},
Milestone MSA3.4.2, 2010, EGEE-III project,
https://edms.cern.ch/ui/file/1062487/2/EGEE-III-MSA3.4.2-1062487-v1\_4.pdf

@@

\bibitem{cordis:etics}
\emph{E-Infrastructure for Testing, Integration and Configuration of Software
(ETICS)} project, European Community Research and Development Information
Service (CORDIS), http://cordis.europa.eu/project/rcn/80138\_en.html

\bibitem{cordis:etics2}
\emph{E-Infrastructure for Testing, Integration and Configuration of Software -
Phase 2 (ETICS 2)} project, European Community Research and Development
Information Service (CORDIS),
http://cordis.europa.eu/project/rcn/86604\_en.html

@@

\bibitem{cordis:emi}
\emph{European Middleware Initiative (EMI)} project, European Community
Research and Development Information Service (CORDIS),
http://cordis.europa.eu/project/rcn/95311\_en.html

\bibitem{iso-9126}
\emph{ISO/IEC 9126 Software Engineering - Product Quality}, International
Organization for Standarization, https://www.iso.org/standard/22749.html

\bibitem{emi-metrics}
\emph{EMI Metrics Specification}, https://goo.gl/CCtY7x

\bibitem{emi-quality-model}
\emph{EMI Quality Model}. Available: https://goo.gl/LdS6fL

\bibitem{cordis:egi-inspire}
\emph{European Grid Initiative: Integrated Sustainable Pan-European
Infrastructure for Researchers in Europe (EGI-InSPIRE)} project, European
Community Research and Development Information Service (CORDIS),
http://cordis.europa.eu/project/rcn/95923\_en.html

\bibitem{egi-ops}
\emph{EGI Operations Portal},
https://operations-portal.egi.eu/

\bibitem{ggus}
\emph{GGUS} EGI Helpdesk,
https://ggus.eu/

\bibitem{gocdb}
\emph{GOCDB} EGI Grid Configuration Repository,
https://ggus.eu/

\bibitem{github}
\emph{GITHUB},
https://github.com/

\bibitem{jenkins}
\emph{Jenkins} Continuous Integration System,
https://jenkins-ci.org/

\bibitem{egi-qc}
\emph{EGI Quality Criteria}. Available: http://egi-qc.github.io/

@@

\bibitem{cordis:egi-engage}
\emph{Engaging the EGI Community towards an Open Science Commons (EGI-ENGAGE)}
project, European Community Research and Development Information Service
(CORDIS), http://cordis.europa.eu/project/rcn/194937\_en.html

\bibitem{cordis:indigo}
\emph{INtegrating Distributed data Infrastructures for Global ExplOitation
(INDIGO--DataCloud)} project, European Community Research and Development
Information Service (CORDIS),
http://cordis.europa.eu/project/rcn/194882\_en.html

\bibitem{indigo-dockerhub}
\emph{INDIGO--DataCloud DockerHub repository},
https://hub.docker.com/u/indigodatacloud

\bibitem{indigo-d31}
\emph{Initial Plan for WP3} INDIGO--DataCloud Deliverable 3.1,
https://www.indigo-datacloud.eu/documents/initial-plan-wp3-d31

\bibitem{indigo-jenkins}
\emph{INDIGO--DataCloud Jenkins CI service},
https://jenkins.indigo-datacloud.eu:8080/

\bibitem{indigo-github}
\emph{INDIGO--DataCloud GitHub Source Code repository},
https://www.github.com/indigo-dc

\bibitem{indigo-gitbook}
\emph{INDIGO--DataCloud GitBook Documentation repository},
https://www.gitbook.com/@indigo-dc

\bibitem{indigo-puppet}
\emph{INDIGO--DataCloud PuppetForge repository},
https://forge.puppet.com/indigodc

\bibitem{indigo-galaxy}
\emph{INDIGO--DataCloud Ansible Galaxy repository},
https://galaxy.ansible.com/indigo-dc/

\bibitem{indigo-ansible}
\emph{INDIGO--DataCloud Ansible Galaxy repository},
https://galaxy.ansible.com/indigo-dc/

\bibitem{grimoirelab}
\emph{GrimoireLab}, http://grimoirelab.github.io/

\bibitem{indigo-pkg-repo}
\emph{INDIGO--DataCloud Linux Package repository}, https://jenkins.indigo-datacloud.eu/

\bibitem{ggus}
\emph{Global Grid User Support (GGUS)}, https://www.ggus.eu/

>>>>

\bibitem{cordis:datagrid}
\emph{DataGrid project}, European Community Research and Development
Information Service (CORDIS) [Online]. Available: http://cordis.europa.eu/project/rcn/53665\_en.html

@@

\bibitem{agile-manifesto}
\emph{Manifesto for Agile Software Development} [Online]. Available: http://agilemanifesto.org

@@

\bibitem{cordis:egee}
\emph{Enabling Grids for E-sciencE (EGEE)} project, European Community
Research and Development Information Service (CORDIS) [Online]. Available: 
http://cordis.europa.eu/project/rcn/80149\_en.html

\bibitem{cordis:egee2}
\emph{Enabling Grids for E-sciencE-II (EGEE-II)} project, European Community
Research and Development Information Service (CORDIS) [Online]. Available: 
http://cordis.europa.eu/project/rcn/99189\_en.html

\bibitem{cordis:egee3}
\emph{Enabling Grids for E-sciencE-III (EGEE-III)} project, European Community
Research and Development Information Service (CORDIS) [Online]. Available: 
http://cordis.europa.eu/project/rcn/87264\_en.html

\bibitem{egee:acceptance-criteria}
\emph{Definition and Documentation of the Revised Software Life-Cycle Process},
Milestone MSA3.4.2, 2010, EGEE-III project [Online]. Available: https://edms.cern.ch/ui/file/1062487/2/EGEE-III-MSA3.4.2-1062487-v1\_4.pdf

@@

\bibitem{cordis:etics}
\emph{E-Infrastructure for Testing, Integration and Configuration of Software
(ETICS)} project, European Community Research and Development Information
Service (CORDIS) [Online]. Available: http://cordis.europa.eu/project/rcn/80138\_en.html

\bibitem{cordis:etics2}
\emph{E-Infrastructure for Testing, Integration and Configuration of Software -
Phase 2 (ETICS 2)} project, European Community Research and Development
Information Service (CORDIS), [Online]. Available: http://cordis.europa.eu/project/rcn/86604\_en.html

@@

\bibitem{cordis:emi}
\emph{European Middleware Initiative (EMI)} project, European Community
Research and Development Information Service (CORDIS) [Online]. Available: 
http://cordis.europa.eu/project/rcn/95311\_en.html

\bibitem{iso-9126}
\emph{ISO/IEC 9126 Software Engineering - Product Quality}, International
Organization for Standarization [Online]. Available: https://www.iso.org/standard/22749.html

\bibitem{emi-metrics}
\emph{EMI Metrics Specification} [Online]. Available: https://goo.gl/CCtY7x

\bibitem{emi-quality-model}
\emph{EMI Quality Model} [Online]. Available: https://goo.gl/LdS6fL

\bibitem{cordis:egi-inspire}
\emph{European Grid Initiative: Integrated Sustainable Pan-European
Infrastructure for Researchers in Europe (EGI-InSPIRE)} project, European
Community Research and Development Information Service (CORDIS) [Online]. Available: 
http://cordis.europa.eu/project/rcn/95923\_en.html

\bibitem{egi-ops}
\emph{EGI Operations Portal} [Online]. Available: 
https://operations-portal.egi.eu/

\bibitem{ggus}
\emph{GGUS} EGI Helpdesk [Online]. Available: 
https://ggus.eu/

\bibitem{gocdb}
\emph{GOCDB} EGI Grid Configuration Repository [Online]. Available: 
https://ggus.eu/

\bibitem{github}
\emph{GITHUB} [Online]. Available: 
https://github.com/

\bibitem{jenkins}
\emph{Jenkins} Continuous Integration System [Online]. Available: 
https://jenkins-ci.org/

\bibitem{egi-qc}
\emph{EGI Quality Criteria} [Online]. Available: http://egi-qc.github.io/

@@

\bibitem{cordis:egi-engage}
\emph{Engaging the EGI Community towards an Open Science Commons (EGI-ENGAGE)}
project, European Community Research and Development Information Service
(CORDIS), [Online]. Available:  http://cordis.europa.eu/project/rcn/194937\_en.html

\bibitem{cordis:indigo}
\emph{INtegrating Distributed data Infrastructures for Global ExplOitation
(INDIGO--DataCloud)} project, European Community Research and Development
Information Service (CORDIS) [Online]. Available: 
http://cordis.europa.eu/project/rcn/194882\_en.html

\bibitem{indigo-dockerhub}
\emph{INDIGO--DataCloud DockerHub repository} [Online]. Available: 
https://hub.docker.com/u/indigodatacloud

\bibitem{indigo-d31}
\emph{Initial Plan for WP3} INDIGO--DataCloud Deliverable 3.1 [Online]. Available: 
https://www.indigo-datacloud.eu/documents/initial-plan-wp3-d31

\bibitem{indigo-jenkins}
\emph{INDIGO--DataCloud Jenkins CI service} [Online]. Available: 
https://jenkins.indigo-datacloud.eu:8080/

\bibitem{indigo-github}
\emph{INDIGO--DataCloud GitHub Source Code repository} [Online]. Available: 
https://www.github.com/indigo-dc

\bibitem{indigo-gitbook}
\emph{INDIGO--DataCloud GitBook Documentation repository} [Online]. Available: 
https://www.gitbook.com/@indigo-dc

\bibitem{indigo-puppet}
\emph{INDIGO--DataCloud PuppetForge repository} [Online]. Available: 
https://forge.puppet.com/indigodc

\bibitem{indigo-galaxy}
\emph{INDIGO--DataCloud Ansible Galaxy repository} [Online]. Available: 
https://galaxy.ansible.com/indigo-dc/

\bibitem{indigo-ansible}
\emph{INDIGO--DataCloud Ansible Galaxy repository} [Online]. Available: 
https://galaxy.ansible.com/indigo-dc/

\bibitem{grimoirelab}
\emph{GrimoireLab} [Online]. Available: http://grimoirelab.github.io/

\bibitem{indigo-pkg-repo}
\emph{INDIGO--DataCloud Linux Package repository} [Online]. Available: https://jenkins.indigo-datacloud.eu/

\bibitem{ggus}
\emph{Global Grid User Support (GGUS)} [Online]. Available: https://www.ggus.eu/
